\documentclass[twoside]{article}
\usepackage{amsmath,amssymb,amsthm,graphicx}
\usepackage{epsfig}
\usepackage[authoryear]{natbib}
\bibliographystyle{unsrtnat}
\usepackage{geometry}
\usepackage{setspace}

\geometry{twoside,
          letterpaper, % i.e, paperwidth=210mm and paperheight=297mm,
          top=25mm,
          bottom=45mm,
          left=25mm,
          right=25mm,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5cm}
% Local Macros Put your favorite macros here that don't appear in
% stat-macros.tex.  We can eventually incorporate them into
% stat-macros.tex if they're of general use.

\begin{document}

\textbf{Reflection - Bayesian Evaluation - Talts et al.}\\
\textbf{Nicholas Hoernle \hfill \today}

\begin{enumerate}
\item The paper addresses the suitability of an inference algorithm for a given generative model. It is important in that we should diagnose whether a problem stems from a poorly specified model or from the inference over the parameters in that model. This technique helps us to evaluate whether a given inference algorithm is appropriate for a specified model or not.
\item Critically we do not tackle the fit of an inference model and algorithm to a given dataset. There is no consideration of whether a posterior distribution would be suitable for a given situation or not.
\item We expect a uniform distribution in Figure 13. Rather we see a strongly skewed right distribution. This suggests that the posterior samples for $\beta$ are greater than the prior draw of $\beta$. We are therefore biasing inference through the inference scheme and this can result in misleading conclusions.
\end{enumerate}
\end{document}
